---
title: "MBRP - BaseLine - Full Analysis"
author: "Leonardo Martins"
date: "11 de fevereiro de 2016"
output:
  pdf_document:
    toc: yes
  html_document:
    fig_caption: yes
    fig_height: 7
    fig_width: 9
    keep_md: yes
    toc: yes
---

This is a public document with all scripts used  manuscript: 


All files used here are availible in a public repository licensed under MIT Licences and accessible by the following url:

https://github.com/crepeia/MBRP


#Preparing new analysis

#Loading required packages
```{r, message=FALSE, warning=FALSE}
require(foreign) # Read data stored SPSS
require(car) #Recode Variables
require(psych) #Psychometrics
require(lavaan) #Confirmatory and SEM
require(semPlot) # Plots for SEM
require(semTools) # Comparing SEM models
require(ggplot2) # Plots
require(Hmisc)
```

```{r, message=FALSE, warning=FALSE}
#Setting Directory
setwd("~/MBRP_R")

#Importing SPSS file .sav
base.dat <- read.spss("Base.sav", to.data.frame = T, use.missings = T)

#Recode Missing Data 888
for (i in c(1:350)) {
base.dat[,c(i)]<-sub("888", "NA", base.dat[,c(i)], ignore.case = FALSE, perl = FALSE, fixed = F, useBytes = FALSE)
}

#Recode Missing Data 777
for (i in c(1:350)) {
base.dat[,c(i)]<-sub("777", "NA", base.dat[,c(i)], ignore.case = FALSE, perl = FALSE, fixed = F, useBytes = FALSE)
}

#Creating a subset for analysis without cases excluded in our baseline
MBRP <- base.dat[grep("CORRI", base.dat$ETAPA), ]

#Selecting variable for this work 
MBRP_baseline <- MBRP[ ,c(9,11,12,19,24,245:252,265,266,295:298,299:311,325,326,347:350)]

MBRP_baseline$FFMQTOTAL<-as.numeric(MBRP_baseline$FFMQTOTAL)

#Removing NA from FFMQ Total
MBRP_baseline <- subset(MBRP_baseline, !is.na(MBRP_baseline$FFMQTOTAL))

#Summary 
summary(MBRP_baseline$FFMQTOTAL)

#Recode Mindfulness FFMQ into High and Low
MBRP_baseline$FFMQgroup[MBRP_baseline$FFMQTOTAL< 121] <- "Baixo"
MBRP_baseline$FFMQgroup[MBRP_baseline$FFMQTOTAL>= 121] <- "Altos"
```

#Descriptive
```{r}
#Summary 
summary(MBRP_baseline$FFMQTOTAL)

#FFMQ Groups (High and Low based on median cut off)
as.factor(MBRP_baseline$FFMQgroup)
describe(MBRP_baseline$FFMQgroup)

##Gender
as.factor(MBRP_baseline$X.1Gênero)
describe(MBRP_baseline$X.1Gênero)

##Educational Study
as.factor(MBRP_baseline$X.7.1RECODEEscolaridade)
describe(MBRP_baseline$X.7.1RECODEEscolaridade)

##Meditation
as.factor(MBRP_baseline$X.11.1Vocêpraticameditação)
describe(MBRP_baseline$X.11.1Vocêpraticameditação)

#Age
MBRP_baseline$X.2Idade<-as.numeric(MBRP_baseline$X.2Idade)
summary(MBRP_baseline$X.2Idade)
sd(MBRP_baseline$X.2Idade)
```

```{r, message=FALSE, warning=FALSE}
#Dataframe
MBRP_base <- MBRP_baseline[,c(39,1,14,33,34,16,17,20,21,22:32,35:38,6:13)]

#As dataframe
MBRP_base<-as.data.frame(MBRP_base)

#As factor
MBRP_base[,c(1)]<-as.factor(MBRP_base[,c(1)])

#As numeric
for (i in c(2:32)) {
MBRP_base[,c(i)]<-as.numeric(MBRP_base[,c(i)])
}

# x for correlation matrix
x<-MBRP_base[32]
```


#Comparing Means - Multiple t-tests 

#Tobacco Variables
```{r}
#Descriptive
lapply(MBRP_base[,c(2,3)], function(x) describeBy(x, group =MBRP_base$FFMQgroup))
#Test T
lapply(MBRP_base[,c(2,3)], function(x) t.test(x ~ MBRP_base$FFMQgroup))
#Boxplot Order
paste(names(MBRP_base[,c(2,3)]), sep=",")
lapply(MBRP_base[,c(2,3)], function(x) boxplot(x~FFMQgroup, data=MBRP_base, main="Boxplot", xlab="FFMQ Group", ylab="Check Order Above"))
#Correlation
print(corr.test(x,MBRP_base[2:3]), short=F)
```

#QSU - Urge Variables 
```{r}
#Descriptive
lapply(MBRP_base[,c(4,5)], function(x) describeBy(x, group =MBRP_base$FFMQgroup))
#Test T
lapply(MBRP_base[,c(4,5)], function(x) t.test(x ~ MBRP_base$FFMQgroup))
#Boxplot Order
paste(names(MBRP_base[,c(4,5)]), sep=",")
lapply(MBRP_base[,c(4,5)], function(x) boxplot(x~FFMQgroup, data=MBRP_base, main="Boxplot", xlab="FFMQ Group", ylab="Check Order Above"))
#Correlation
print(corr.test(x,MBRP_base[4:5]), short=F)
```

#HAD e HAS
```{r}
#Descriptive
lapply(MBRP_base[,c(6,7)], function(x) describeBy(x, group =MBRP_base$FFMQgroup))
#Teste T
lapply(MBRP_base[,c(6,7)], function(x) t.test(x ~ MBRP_base$FFMQgroup))
#Boxplot Order
paste(names(MBRP_base[,c(6,7)]), sep=",")
lapply(MBRP_base[,c(6,7)], function(x) boxplot(x~FFMQgroup, data=MBRP_base, main="Boxplot", xlab="FFMQ Group", ylab="Check Order Above"))
#Correlation
print(corr.test(x,MBRP_base[6:7]), short=F)
```


#PANAS - Positive and Negative
```{r}
#Descriptive
lapply(MBRP_base[,c(8,9)], function(x) describeBy(x, group =MBRP_base$FFMQgroup))
#Teste T
lapply(MBRP_base[,c(8,9)], function(x) t.test(x ~ MBRP_base$FFMQgroup))
#Boxplot Order
paste(names(MBRP_base[,c(8,9)]), sep=",")
lapply(MBRP_base[,c(8,9)], function(x) boxplot(x~FFMQgroup, data=MBRP_base, main="Boxplot", xlab="FFMQ Group", ylab="Check Order Above"))
#Correlation
print(corr.test(x,MBRP_base[8:9]), short=F)
```

#PANAS - Sub-escales
```{r}
#Descriptive
lapply(MBRP_base[,c(10:20)], function(x) describeBy(x, group =MBRP_base$FFMQgroup))
#Teste T
lapply(MBRP_base[,c(10:20)], function(x) t.test(x ~ MBRP_base$FFMQgroup))
#Boxplot Order
paste(names(MBRP_base[,c(10:20)]), sep=",")
lapply(MBRP_base[,c(10:20)], function(x) boxplot(x~FFMQgroup, data=MBRP_base, main="Boxplot", xlab="FFMQ Group", ylab="Check Order Above"))
#Correlation
print(corr.test(x,MBRP_base[10:20]), short=F)
```

#CESD
```{r}
#Descriptive
lapply(MBRP_base[,c(21:24)], function(x) describeBy(x, group =MBRP_base$FFMQgroup))
#Teste T
lapply(MBRP_base[,c(21:24)], function(x) t.test(x ~ MBRP_base$FFMQgroup))
#Boxplot Order
paste(names(MBRP_base[,c(21:24)]), sep=",")
lapply(MBRP_base[,c(21:24)], function(x) boxplot(x~FFMQgroup, data=MBRP_base, main="Boxplot", xlab="FFMQ Group", ylab="Check Order Above"))
#Correlation
print(corr.test(x,MBRP_base[21:24]), short=F)
```

#Correlation
```{r}
print(corr.test(x,MBRP_base[2:24]), short=F)
```

